---
title: "Basic analysis of pilot data"
output:
  html_notebook:
    toc: true
    theme: united
    code_folding: hide
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: Adrian Radillo
---

<!-- 
executing  *Cmd+Shift+Enter*. 
Add a new chunk *Cmd+Option+I*.
*Cmd+Shift+K* to preview the HTML file -->
Note how, for now, this code uses data produced from [this code](https://github.com/TheGoldLab/SingleCP_DotsReversal_Task/releases/tag/pilot2).
```{r echo=FALSE, results='hide'}
library(data.table) # see https://cran.r-project.org/web/packages/data.table/vignettes/datatable-intro.html for reference
library(ggplot2)
dataTag <- "pilot2"
datafile <- paste("~/programing/data/psychophys/",dataTag,".csv",sep='')
data <- fread(file=datafile, header=TRUE, sep=",")
# uncomment next line to inspect data table
# str(data)
```
## Basic questions that we may ask
### How long did the session last?
```{r}
cat( round(data[,sum(trialEnd - trialStart)] / 60, digits = 2), "min" )
```

### How many trials were produced?
```{r}
numTrials <- length(unique(data$trialIndex))
# display warning if somehow a trial or more are duplicated
duplicates <- numTrials != nrow(data)
if (duplicates) {
  print("some trials are duplicated -- remainder of notebook should NOT be executed")
} else {
  cat(numTrials, "trials")
}
```

### How many trials were produced per combination of factors? 
```{r echo=FALSE}
# ARGS:
#   initTable       initial data.table object
#   groupVarNames   vector of column names to use for grouping
# RETURNS:
#   combFactors     data.table with unique rows and their frequencies (i.e. count)
getFreq <- function(initTable, groupVarNames) {
  # create a smaller data table only containing the independent variables
  df <- initTable[, ..groupVarNames]

  # create other data table which counts trials with similar indep. vars. values (freq. column)
  combFactors <- df[, .N, by=names(df)]
  setnames(combFactors, c(groupVarNames, "freq."))
  return(combFactors)
}
```

```{r}
indepVarNames <- c("initDirection","presenceCP","coherence","viewingDuration","probCP","timeCP")
combFactors <- getFreq(data, indepVarNames)
combFactors
```

### What were the marginal frequencies?
```{r}
for (i in 1:length(indepVarNames)) {
  print(getFreq(data, indepVarNames[i]))
}
```

### What is the accuracy on the task?
```{r}
accuracy <- sum(data[,correct])/numTrials
cat(accuracy * 100,"%", sep = '')
```
#### Accuracy on CP vs. non-CP trials
```{r}
# count CP and Non-CP trials
cpGrouping <- getFreq(data, "presenceCP")
numCPtrials <- cpGrouping[presenceCP == 1, freq.]
numNonCPtrials <- cpGrouping[presenceCP == 0, freq.]

# compute accuracies in each group of trials
accuracy_CP <- sum(data[presenceCP == 1, correct])/numCPtrials * 100
accuracy_nonCP <- sum(data[presenceCP == 0, correct])/numNonCPtrials * 100
# round to 2 decimals
accuracy_CP <- round(accuracy_CP, digits = 2)
accuracy_nonCP <- round(accuracy_nonCP, digits = 2)

# display summarizing table
toDisplay <- cpGrouping[, ("accuracy") := data.frame("accuracy"=c(accuracy_nonCP, accuracy_CP))]
print(toDisplay)
toDisplay # print a second time because of a bug that I don't fully understand (see https://github.com/IRkernel/IRkernel/issues/127 and https://github.com/rstudio/rmarkdown/issues/1002)
```

#### Accuracy as a function of viewing duration
```{r}
# first get marginal frequencies
toDisplay <- data[order(viewingDuration),.(freq = .N, correct = sum(correct)), by=viewingDuration]

# then add the accuracy column
toDisplay <- toDisplay[,.(viewingDuration, freq, correct, accuracy = round(correct/freq*100,digits=2))]
toDisplay
```

#### Accuracy as a function of coherence level
```{r}
# first get marginal frequencies
toDisplay <- data[order(coherence),.(freq = .N, correct = sum(correct)), by=coherence]

# then add the accuracy column
toDisplay <- toDisplay[,.(coherence, freq, correct, accuracy = round(correct/freq*100,digits=2))]
toDisplay
```

#### Group by change point presence after CP time
For viewing durations greater than the change point time, compare accuracies between CP and non-CP trials
```{r}
# first get marginal frequencies
toDisplay <- data[viewingDuration > .2,
                  .(freq = .N, correct = sum(correct)), 
                  by=.(viewingDuration, presenceCP)]
# then add the accuracy column
toDisplay <- toDisplay[,.(viewingDuration, freq, correct, presenceCP,  accuracy = round(correct/freq*100,digits=2))]
toDisplay
```
### How precise were the dots timings?
We plot `(dotsOff - dotsOn) - viewingDuration`, across all trials.
```{r}
axes_labels_font <- 18
axes_font <- 15
durTable <- data[,.(dotsDurationError = (dotsOff - dotsOn - viewingDuration) * 1000, presenceCP, viewingDuration)]
g <- ggplot(durTable, aes(x=1:nrow(durTable), y=dotsDurationError)) + 
  geom_line(size=.2) +  geom_point(aes(shape=factor(presenceCP),
                                       col=factor(viewingDuration)),size=3) 
# Add Title and Labels
g + labs(title="Error in generated dots duration", 
         subtitle=paste("From",dataTag,"dataset",sep=" "), 
         y="duration error (msec)", 
         x="trial (in session order)",
         color="viewing dur.", shape="CP") + theme(plot.title=element_text(size=20, 
                                    family="American Typewriter",
                                    color="tomato",
                                    lineheight=1.2),  # title
            plot.subtitle=element_text(size=15, 
                                       family="American Typewriter"),  # subtitle
            plot.caption=element_text(size=15),  # caption
            axis.title.x=element_text(size=axes_labels_font),  # X axis title
            axis.title.y=element_text(size=axes_labels_font),  # Y axis title
            axis.text.x=element_text(size=axes_font),  # X axis text
            axis.text.y=element_text(size=axes_font))  # Y axis text
```
Note how the largest errors (roughly 40msec) occur on longest viewing duration trials which contain a change point (blue triangles).

Also, there seems to be 3 main error magnitudes (see `meanDurationError` column below). With an approximate frame rate of 60, we present in `num_frames` the approximate number of frames for these three durations.
```{r}
# note, it might be ideal to leverage the following package
# library("pomp2")
# see documentation for pomp2 package
# pdf: file:///home/adrian/Downloads/v69i12.pdf
# website: https://kingaa.github.io/pomp/vignettes/upgrade_guide.html

# for now, very simple algo.
# bin duration errors into 3 bins
intervals <- bin(durTable[,.(dotsDurationError)], nbins = 3, method = "cluster")
names(intervals) <- "interval"

# add the bins as a factor to the data.table
durTable[, ("interval") := intervals]

# compute mean durations
unordered <- durTable[, .(num_trials=.N, meanDurationError = mean(dotsDurationError)), by = intervals]

# display results, with num_frame column
frameRate <- 60
unordered[order(meanDurationError),.(num_trials, meanDurationError, num_frames = (meanDurationError * frameRate / 1000))]
```


### Explore random seed
```{r}
axes_labels_font <- 18
axes_font <- 15
seedTable <- data[,.(randSeedBase,trialIndex)]
g <- ggplot(seedTable, aes(x=1:nrow(seedTable), y=randSeedBase)) + 
  geom_line(size=.2) #+  geom_point(aes(shape=factor(presenceCP), col=factor(viewingDuration)),size=3) 

# Add Title and Labels
g + labs(title="Random seed base", 
         subtitle=paste("From",dataTag,"dataset",sep=" "), 
         y="randSeedBase", 
         x="trial (in session order)") + theme(plot.title=element_text(size=20, 
                                    family="American Typewriter",
                                    color="tomato",
                                    lineheight=1.2),  # title
            plot.subtitle=element_text(size=15, 
                                       family="American Typewriter"),  # subtitle
            plot.caption=element_text(size=15),  # caption
            axis.title.x=element_text(size=axes_labels_font),  # X axis title
            axis.title.y=element_text(size=axes_labels_font),  # Y axis title
            axis.text.x=element_text(size=axes_font),  # X axis text
            axis.text.y=element_text(size=axes_font))  # Y axis text
```

