---
title: "Mixed Effects Logistic Regressions"
output:
  html_document:
    df_print: paged
    code_folding: hide
---
```{r}
library(data.table)
library(ggplot2)
source("../REF_FUNCTIONS/process.r")
```

```{r}
DATA_FOLDER <- '/home/adrian/SingleCP_DotsReversal/Fall2019/raw/'
```

```{r}
#t1 <- fread(paste0(DATA_FOLDER, 'completed4AFCtrials_task99_date_2019_11_05_10_27.csv'))
full_data <- get_full_data(paste0(DATA_FOLDER, 'full_2019_12_02.csv'))
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r}
str(full_data)
```

What viewing duration has the most data?

```{r}
ggplot(full_data[,.(numTrials=.N), by=.(subject, duration, probCP, presenceCP)], aes(x=duration, y=numTrials, col=presenceCP)) + 
  geom_point() + 
  facet_grid(subject~probCP) +
  scale_color_manual(values=c(cbbPalette[8], cbbPalette[6]))
```
Let's stick to 200 msec for now.
```{r}
full_data_200 <- full_data[duration == 200]
```

```{r}
full_data_200[, scoh := coherence]
full_data_200[direction=="left", scoh := -coherence]
```

Now, let's plot the raw data per subject, per probCP (i.e. session). 

```{r}
psychom <- full_data_200[, `:=`(propChoseR=sum(dirChoice=="right")/.N, trialCount=.N), by=.(subject, probCP, scoh)]
psychom[,dataCount:="<3"]
psychom[trialCount >= 3 & trialCount < 10, dataCount:="<10"]
psychom[trialCount >= 10 & trialCount < 20, dataCount:="<20"]
psychom[trialCount >= 20, dataCount:=">=20"]
psychom[,dataCount := factor(dataCount, levels=c("<3", "<10", "<20", ">=20"))]
```

```{r, fig.width=7, fig.height=7}
ggplot(psychom, aes(x=scoh, y=propChoseR)) + 
  geom_point(size=3, aes(shape=dataCount)) +
  geom_hline(yintercept = c(0,.5,1), linetype='dashed') +
  facet_grid(subject~probCP) +
  theme(text=element_text(size=17))
```

Given the extremely low number of trials at 100% coherence, it might be better to pool all trials at 100% coherence lasting 200 msec or more, for noCP trials, for a given session, to estimate the lapse rate. By lapse rate, I mean the probability of making the wrong choice on a 100%-coherence trial.

```{r}
lapse_data <- full_data[duration >= 200 & coh_cat == "100" & presenceCP == "noCP"]
lapse_data[, wrong:=(dirChoice != direction)]
lapse_data[, `:=`(lapse=sum(wrong) / .N, numTrials=.N), by=.(subject, probCP)]
```

```{r}
ggplot(lapse_data, aes(x=subject, y=numTrials, group=probCP, col=probCP)) + geom_point() +
  scale_color_manual(values=c(cbbPalette[8], cbbPalette[6]))
```

```{r}
# lapse_data[, scoh := coherence]
# lapse_data[direction=="left", scoh := -coherence]
```

```{r}
ggplot(lapse_data, aes(x=subject, y=lapse, col=probCP)) + geom_point(size=4, aes(shape=probCP)) +
  scale_color_manual(values=c(cbbPalette[8], cbbPalette[6]))
```

These are the MLEs for the lapse parameters of each subject on each session (estimated on trials of 200-msec or longer, with no CP).

Now, I want to fit the logistics to the non-100%-coh choice data, using the estimated lapse values above.

Let's start with a single session for now. Say, subject 10, probCP = 0.7.
```{r}
# logistic fit for single session, after lapse has been estimated 
logistic_fit_separate_lapse <- function(subj, pcp, dur, lapse_data_table, full_data_table) {
  # 1/ get raw data for session (fix VD, probCP and subject)
  # subj <- "12"
  # pcp <- "0.3"
  # dur <- 200
  
  # fetch lapse value
  lapse <- lapse_data_table[duration == dur & probCP == pcp & subject == subj, lapse][1]
  
  raw_data <- full_data_table[duration == dur & probCP == pcp & subject == subj]
  raw_data[, scoh := coherence]
  raw_data[direction == "left", scoh := -coherence]
  
  # 3/ compute proportions and number of trials
  raw_data[, `:=`(propChoseR=sum(dirChoice=="right")/.N, trialCount=.N), by=scoh]
  
  # 2/ exclude 100%-coh trials from data
  raw_data_no100 <- raw_data[coh_cat != "100"]
  
  # 4/ transform proportions according to lapse
  
  # args:
  #     prop   = true proportion of choosing Right side
  #     l      = estimated lapse rate
  # returns:
  #     transformed proportion which can be used to fit a logistic
  fwd_lapse_transform <- function(prop, l) {
    return((prop - l)/(1-2*l))
  }
  
  # args:
  #     tprop  = transformed proportion of choosing Right side
  #     l      = estimated lapse rate
  # returns:
  #     true proportion of choosing Right side
  bwd_lapse_transform <- function(tprop, l) {
    return(tprop*(1-2*l) + l)
  }
  
  raw_data_no100[, tprop:=fwd_lapse_transform(propChoseR, lapse)]
  tofit <- unique(raw_data_no100[,.(scoh, right=round(tprop*trialCount), left=trialCount-round(tprop*trialCount))])
  
  # 5/ fit glm using propotions!
  fit <- glm(cbind(right, left) ~ scoh, data = tofit, family = binomial(logit))
  
  # 6/ get glm prediction     &     7/ transform back to real proportions
  pred_base <- data.table(scoh=seq(-100,100))
  pred_base[, `:=`(propChoseR=bwd_lapse_transform(predict(fit, newdata=pred_base, type="response"), lapse),
                   subject=subj, probCP=pcp)]
  
  return(list(raw_data, pred_base))
}


# 8/ plot full raw dataset for session (including 100%-coh trials) and psychometric fit
# ggplot(raw_data, aes(x=scoh, y=propChoseR)) + 
#   theme_bw() + 
#   geom_line(data=pred_base, size=1.3) + 
#   geom_point(colour="brown1", size=4) + # geom_errorbar(aes(ymin=propRight-ci, ymax=propRight+ci), colour="brown1", width=3) +
#   geom_hline(yintercept = c(0,0.5,1), linetype="dashed") + geom_vline(xintercept = 0, linetype="dashed") + 
#   scale_y_continuous(name = "P(choose R)", breaks = c(0,0.5,1), limits = c(0,1)) +
#   labs(title="Psychometric function on noCP trials", subtitle = "Fall 2019", caption=paste('subj:', subj, ' VD:', dur, 'ms', ' prob(CP):', pcp)) +
#   theme(text=element_text(size=20), plot.title = element_text(hjust=0.5)) 
```

And all subjects:
```{r}
# # ARGS:
# #  subj         string for level of subject column
# #  base_data    data.table with data from all subjects
# logistic_plot <- function(subj, vd, base_data) {
#   # fit logistic regression
#   subj_base_data <- base_data[subject==subj]
#   fitted <- glm(data = subj_base_data, formula = dirChoice ~ scoh, family = binomial(link = logit))
#   pred_base <- data.table(scoh=seq(-100,100,10))
#   pred_base[, `:=`(propRight=predict(fitted, newdata=pred_base, type="response"), 
#                    subject=subj,
#                    duration=vd)]
#   
#   # this is a data.table with only the proportion choose right data
#   new_data <- subj_base_data[,.(propRight=sum(dirChoice=='right')/.N, numTrials=.N), by=.(scoh)]
#   new_data[,`:=`(ci=1.96*sqrt(propRight*(1-propRight)/numTrials), 
#                  subject=subj,
#                  duration=vd)]
#   
#   tot_zeros = subj_base_data[scoh==0, .N]
#   num_zero_right = subj_base_data[scoh==0 & direction=="right", .N]
#   
#   return(list(new_data, pred_base, round(num_zero_right/tot_zeros, 2)))
# }

subjects_list <- unique(full_data[,subject])
numSubjects <- length(subjects_list)
numPcp <- 2  # 0.3 and 0.7
#numVD <- length(unique(full_data[, duration]))
dt1 <- vector(mode = "list", length = numSubjects*numPcp - 1)  # for choice proportion data
dt2 <- vector(mode = "list", length = numSubjects*numPcp - 1)  # for fitted curves

counter <- 1
vdur <- 200
for (ss in subjects_list) {
  for (prob_cp in c("0.3", "0.7")) {
    if ((ss == "10") & (prob_cp == "0.3")) {
      next
    }
    returned <- logistic_fit_separate_lapse(ss, prob_cp, vdur, lapse_data, full_data)  
    dt1[counter] <- returned[1]
    dt2[counter] <- returned[2]
    counter <- counter + 1
  }
}

new_data <- rbindlist(dt1)
pred_base <- rbindlist(dt2)

new_data[, `:=`(probCP=as.factor(probCP), subject=as.factor(subject))]
pred_base[, `:=`(probCP=as.factor(probCP), subject=as.factor(subject))]
```

```{r, fig.width=9, fig.height=10}
# plot
gp <- ggplot(new_data, aes(x=scoh, y=propChoseR)) + 
  geom_line(data=pred_base, size=1.3) + 
  geom_point(colour="brown1", size=3) + # geom_errorbar(aes(ymin=propRight-ci, ymax=propRight+ci), colour="brown1", width=3) +
  geom_hline(yintercept = c(0,0.5,1), linetype="dashed") + geom_vline(xintercept = 0, linetype="dashed") + 
  scale_y_continuous(name = "P(choose R)", breaks = c(0,0.5,1), limits = c(0,1)) +
  labs(title="Psychometric functions on noCP 200-msec trials", subtitle = "data from Fall 2019") +
  theme(text=element_text(size=20), plot.title = element_text(hjust=0.5)) +
  facet_grid(subject~probCP)
plot(gp)
```

